\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-16 Latex/paper-resum.tex
Stylish IV

We are going to introduce a general idea of the method. Let us define the process $Z_t = f(x_t)$. Suppose that $Z_t$ is a martingale under the measure $\mathbb{Q}_1$. However, we are interested in calculate $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$ where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left[f(x_t)\right] + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, taking $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and using Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
\end{equation}
The second term is the convexity adjustment due to the change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The different choices of $f$, $\mathbb{Q}_1$, and $\mathbb{Q}_2$ will allow us to obtain a convexity adjustment approximation for the different cases of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. we must note, that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.

@@

In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs. It is common in the market to find two version of these futures, depending on how the fixings of the reference index are using. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
\end{align*}
Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
%\end{align*}
\intertext{and when $t \in  [t_0, t_1]$, we have}
%\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
In order, to clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

@@

The next figure, show accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}). The parameters that we have used to run the Monte Carlo have been $k=0.003$ and volatility $\sigma=0.01$ and flat curve $r=0.01$. 
\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
		\caption{Convexity Avg Mc Vs Convexity Avg Malliavin}
\end{subfigure}
\caption{Convexity adjustment for compounding and average OIS}
\end{figure} 
\end{example}

\subsection{FRAs in arrears}
A FRA in arrears is the most classic example among the products with convexity adjustment. The price is given by 
\begin{equation}\label{FRAinArrear}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left[L_{E}(t_1,t_1,t_2)\right],
\end{equation}
i.e. the cash flow associated to a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{align}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds 
\end{align}
with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
We can restrict the model the the Hull-White model with constant parameters. The analytical approximation that we get from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$, $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{Convexity Mc Vs Convexity Malliavin}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\begin{remark}
Note from \eqref{bond_forward} that
\begin{equation*}
S_{a,b}(t) = S^{ois}_{a,b}(t) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})} {01(t,t_a,t_b)}
\end{equation*}
where 
\begin{equation*}
\alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{1}{\delta_{t^{E}_{i-1}, t^{E}_i}}\left(\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1\right)
\end{equation*}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Given
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
\end{equation}
Then, we have the temporal convexity adjustment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber 
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}

\begin{remark}
The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left( D_s \bar{x}_{t_a}\right)$. The simplest cases are on the Hull-White or Ho-Lee model. The general case is treated in (\ref{approximation_under_annuity_measeure_d_s}). 
\end{remark}

\begin{example}[Convexity adjustment for CMS under the Hull-White model]
To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left(S^{ois}_{a,b}(t_a)\right)$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right)$. For the Hull-White model case, we have that
\begin{equation*}
D_s x_{t_a} = \sigma \exp(-(t_a - s)).
\end{equation*}
and the volatility is only time-dependent i.e 
$$
\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) = 0.
$$
Therefore, \eqref{cms_first_order_convexity} is equal to
\begin{equation*}
\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \frac{\sigma^{2}(1-\exp(-2kt_a))}{2k}.
\end{equation*}

@@

\section{Conclusions}\label{sec:Conclusion}
In the present paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products. Although the convexity adjustment could be calculated using other techniques, Malliavin calculus provides a simple way to get a template for the convexity adjustment. We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model. We have also seen the excellent quality of the numerical accuracy of the formulas obtained.

@@

\section{Auxiliary lemmas}
\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
In order to get the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}. Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$. The role of $\epsilon$ is only as interpolation parameter between process. We will suppose the next parametrization of the Cheyette model
\begin{align}\label{parametric_process}
y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left[y_t\right]= \mathbb{V}ar(x_t)$. Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$. We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$. We will define the next parametrization for $\nu \in [0,1]$

@@

Then we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore

@@

Then we have that

@@

E_{y}(t)= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du

@@

Now, from Cauchy-Schwarz inequality we have that

@@

&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du

@@

In order, to find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then

@@

\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu

@@

We must note that

@@

Then using (\ref{upper_bound_E_y}) we get that

@@

Then from (\ref{upper_bound_E_x}) and (\ref{upper_bound_E_y}) we get that 

>>>>

We are going to introduce a general idea of the method. Let us define the process $Z_t = f(x_t)$. Suppose that $Z_t$ is a martingale under the measure $\mathbb{Q}_1$. However, we are interested in calculate $\mathbb{E}^{\mathbb{Q}_2}\left[Z_T \right]$ where $\mathbb{Q}_2$ is a measure under which $Z_t$ is not martingale and such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left[f(x_t)\right] + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, taking $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and using Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left[ f(x_t) \right] = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left[\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left[ f^{\prime}(x_t) D_s x_t  \right] \lambda_s ds \right]. 
\end{equation}
The second term is the convexity adjustment due to the change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The different choices of $f$, $\mathbb{Q}_1$, and $\mathbb{Q}_2$ will allow us to obtain a convexity adjustment approximation for the different cases of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. Note that $L_{E}(t_0, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$ associated with the numeraire $P_{ois}(t,t_2)$.

@@

In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters used are $\sigma=0.015$, $k=0.003$, and flat curve with level $r=0.01$.

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swaps, also known as STIRs. It is common in the market to find two versions of these futures, depending on how the fixings of the reference index are used. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during the entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
\end{align*}
Before continuing, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
%\end{align*}
\intertext{and when $t \in  [t_0, t_1]$, we have}
%\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
To clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

@@

The following figure shows the accuracy of (\ref{convexity_ois_future}) and (\ref{convexity_avg_ois_future}). The parameters used to run the Monte Carlo have been $k=0.003$, a volatility $\sigma=0.01$, and flat curve $r=0.01$. 
\begin{figure}[H]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_ois.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[scale=0.2]{Figures/convexity_avg_ois.jpg}
		\caption{Convexity Avg Mc Vs Convexity Avg Malliavin}
\end{subfigure}
\caption{Convexity adjustment for compounding and average OIS}
\end{figure} 
\end{example}

\subsection{FRAs in arrears}
A FRA in arrears is the most classic example among convexity adjustment products. The price is given by
\begin{equation}\label{FRAinArrear}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left[L_{E}(t_1,t_1,t_2)\right],
\end{equation}
i.e. the cash flow associated with a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{align}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds 
\end{align}
with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
The model can be restricted to a Hull-White model with constant parameters. The analytical approximation obtained from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$ and $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{Convexity Mc Vs Convexity Malliavin}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\begin{remark}
Note from \eqref{bond_forward} that
\begin{equation*}
S_{a,b}(t) = S^{ois}_{a,b}(t) + \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} \alpha(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})} {01(t,t_a,t_b)}
\end{equation*}
where 
\begin{equation*}
\alpha(t,t^{E}_{i-1}, t^{E}_{i})  = \frac{1}{\delta_{t^{E}_{i-1}, t^{E}_i}}\left(\frac{H(t,t^{E}_{i-1})}{H(t,t^{E}_{i})} - 1\right).
\end{equation*}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Given
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
\end{equation}
Then, we have the temporal convexity adjustment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)}  \\
&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber 
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}

\begin{remark}
The key point is calculate an approximation of $\mathbb{E}_s^{0,1}\left[ D_s \bar{x}_{t_a}\right]$. The simplest cases are on the Hull-White or Ho-Lee model. The general case is treated in (\ref{approximation_under_annuity_measeure_d_s}). 
\end{remark}

\begin{example}[Convexity adjustment for CMS under the Hull-White model]
To check the accuracy of the last approximation, we compute with a Monte Carlo the exact value of $\mathbb{E}^{t_p}\left[S^{ois}_{a,b}(t_a)\right]$ under spot measure $\mathbb{Q}$, i.e we will compute  $\frac{1}{P(0,t_p)}  \mathbb{E}^{\mathbb{Q}}\left[\frac{S_{a,b}(t_a)}{\beta_{t_a}} \right]$. For the Hull-White model case, we have that
\begin{equation*}
D_s x_{t_a} = \sigma \exp(-(t_a - s)).
\end{equation*}
and the volatility is only time-dependent i.e 
$$
\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b)) = 0.
$$
Therefore, \eqref{cms_first_order_convexity} is equal to
\begin{equation*}
\mathbb{E}^{t_p}\left(S_{a,b}(t_a)\right) \approx  S^{ois}_{a,b}(0) + \frac{\partial_x S^{ois}_{a,b}(t_a, \bar{x}_0(t_a),\bar{y}(t_a))\partial_x M(t_a,t_p, \bar{x}_0(t_a),\bar{y}(t_a))}{M(0,t_p)} \frac{\sigma^{2}(1-\exp(-2kt_a))}{2k}.
\end{equation*}

@@

\section{Conclusions}\label{sec:Conclusion}
In the present paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products. Although the convexity adjustment could be calculated using other techniques, Malliavin calculus provides a simple way to get a template for the convexity adjustment. We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model. We have also seen the excellent quality of the numerical accuracy of the formulas obtained.\\

@@

\section{Auxiliary lemmas}
\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
To obtain the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}. Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$. The role of $\epsilon$ is only as an interpolation parameter between the process. We will suppose the next Cheyette model parametrization
\begin{align}\label{parametric_process}
y_{\epsilon,t} &= \int_{0}^{t} \exp\left(-2 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon^{2} \eta^{2}(u,x_{\epsilon,u},y_{\epsilon,u}) du \\
x_{\epsilon, t} &= \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_{\epsilon,u} du + \int_{0}^{t} \exp\left(-\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \epsilon \eta(u,x_{\epsilon,u},y_{\epsilon,u})  \bar{y}_u du
\end{align}
The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left[y_t\right]= \mathbb{V}ar(x_t)$. Therefore, if the scale of $x_{\epsilon,t}$ is $\epsilon$, then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$.\\

We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$. We will define the next parametrization for $\nu \in [0,1]$

@@

Then, we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore,

@@

Moreover, we have that

@@

E_{y}\left[t\right]= 2 \int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \nabla_{x,y}\eta(u, \nu x_u, \nu y_u) \cdot (x_u, y_u) d\nu du

@@

Now, from Cauchy-Schwarz inequality, we obtain that

@@

&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du.

@@

To find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then

@@

\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu.

@@

Note that

@@

Using (\ref{upper_bound_E_y}), we get that

@@

By using \eqref{upper_bound_E_x} and \eqref{upper_bound_E_y}, we have that 
